Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7

### 2019-07-21 paper/ms.tex
paper improvements

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{epdparams_vs_time.png}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		Timeseries of ``external parameters'' for a representative
			star over one sector.
			{\it Top}: Instrumental raw magnitude (with a particular
		aperture size), as a function of time.  {\it Second and third from
			top}: $x$ and $y$ centroid positions as a function of time.
		Continuing in order are the CCD temperature, the $(s,d,k)$ shape
		parameters, and the measured background value.
		Most of the apparent variability is instrumental.
		\label{fig:external_parameter_timeseries}
	}
\end{figure}
The preceding steps produce light curves that include both
instrumental systematics as well as astrophysical variability.  The
detrending approach adopted by the HAT group to remove systematic
variability typically proceeds in a few sequential stages, as
discussed by {\it e.g.} \citet{bakos_2010}, \citet{huang_high-precision_2015},
and \citet{zhang_precision_2016}.

The first detrending step commonly performed on ground-based data is
``magnitude-fitting'': the raw magnitudes measured from the difference
images are fit by a polynomial that depends on a combination of CCD
position, sub-pixel position, and optionally catalog magnitude and
color \citep[][\S~5.5]{zhang_precision_2016}.

The second step is to decorrelate against external parameters that are
known to affect the stellar flux measurements (EPD,
\citealt[][]{bakos_2010}).  For ground-based data this may
include zenith angle, or changing PSF parameters.  For TESS data, this
might include CCD temperature, or the angles of the Moon and Earth
relative to each camera's boresight.
Some example ``external'' parameters that we
include with our light curves are shown as functions of time in
Figure~\ref{fig:external_parameter_timeseries}.

The final step is to then decorrelate the measured brightnesses of
stars against each other (TFA, \citealt{kovacs_trend_2005}).  This
accounts for variations due to unknown systematic instrument changes
that affect many stars.  This latter step is similar to a principal
component analysis of all the light curves, in which the components
are chosen as a subset of the light curves.
In this sense TFA is similar to the Sys-Rem, PDC, and ARC2 methods
\citep{tamuz_correcting_2005,smith_pdc_2012,aigrain_robust_2017}
except that these latter methods make different choices for the basis
vectors, and apply different procedures for determining the
best-fitting coefficients of the linear model.

We explored the possibility of fitting linear models of flux as
functions of {\it e.g.,} temperature, shape parameters, centroid
positions, and stellar colors.  We also briefly explored non-linear
model fitting using $N$-dimensional B-splines to fit the flux,
centroid positions, and temperatures simultaneously
\citep{dierckx_curve_1996}.  The linear models typically underfit the
light curves, particularly during the large shifts that happen as the
spacecraft nears perigee.  The non-linear models showed some promise,
but often seemed to overfit stellar variability signals.  One thought
that we did not try but may explore in future work is to decorrelate
against the standard deviation of the spacecraft quartnerion time-series
\citep{vanderburg_hr858_2019}.

Given these complications, for the time being we omit the step of
``detrending'' as a function of external parameters. To enable further
exploration of the issue, we include all the necessary vectors of {\it
e.g.}, centroid positions, temperatures, and shape parameters in our
reported light curves.

@@

Since most of the external parameter dependence is shared between
stars, we opt instead to decorrelate the flux timeseries of each star
against other stars in the frame.  We use the TFA algorithm proposed
by \citet{kovacs_trend_2005}, which for self-consistency we describe
here.

The idea of the method is as follows.
Suppose we have $M$ ``template stars'', which are a subsample of
stars that represent all types of systematics across the dataset. 
Each template star has a light curve with $N$ data points.
Denote the template time-series $X_j(i)$, where $j={1,\ldots,M}$ and 
$i={1,\ldots,N}$ is the time index.
We then want to find periodic signals in a target time-series $Y(i)$.
This is done by defining a filter function
\begin{equation}
F(i) = \sum_{j=1}^{M} c_j X_j(i),
\end{equation}
for which the coefficients $c_j$ are found by minimizing
\begin{equation}
\mathcal{D} = \sum_{i=1}^{N} \left[ Y(i) - A(i) - F(i) \right]^2.
\label{eq:tfa_to_minimize}
\end{equation}
When trying to find periodic signals, $A(i)$ represents our prior
knowledge of the light curve's shape.
This prior is simply that stars on average maintain a constant brightness:
\begin{equation}
A(i) = \langle Y \rangle = \frac{1}{N} \sum_{i=1}^{N} Y(i) = {\rm const.}
\end{equation}
If a signal is eventually found, for instance using the box-least squares
method \citep{kovacs_box-fitting_2002},
this detrending process must then be repeated while accounting for our
updated knowledge about the light curve's shape.

Once the template stars were selected, we use the \texttt{VARTOOLS}
program to perform the detrending \citep{Hartman_Bakos_2016}.
This process was performed for each photometric aperture
separately.

@@

Figures~\ref{fig:pg1} to~\ref{fig:pg6} of this
section summarize this document. Updated versions and their 
\texttt{README} files will live at this web-address: 
\url{mast.stsci.edu/CDIPS}.
The planet candidate chosen for these figures
(Gaia-DR2 \texttt{5541111035713815552} = TIC \texttt{134528212}) was
chosen for the demonstration in part because it passes all
the tests.
It is one of a number of the giant planet candidates that we note may
be in open clusters.

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page01.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Transit search summary.} Periodograms from TLS and 
		phase-dispersion minimization, as calculated 
		with \texttt{astrobase.periodbase}, are shown in the top left and top center 
		\citep{bhatti_astrobase_2018,hippke_TLS_2019,stellingwerf_period_1978}.
		The top three peaks from each 
		method are shown in the second and third rows; the raw light curve is in the 
		top-right. A small finder chart from DSS is inset to the top left, with
		the 1.5-pixel radius aperture used to extract the light curve in orange.
		\label{fig:pg1}
	}
\end{figure*}

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page02.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Light curve diagnostics.} 
		Time-series of raw flux (\texttt{IRM2}),  TFA-detrended flux (\texttt{TF2}), stellar-variability
		detrended flux, and the background are shown as a function of
		barycentric Julian date.
		The overplotted dashed vertical lines are the ephemeris of the highest-power
		TLS peak from Figure~\ref{fig:pg1}.
		An important check is whether the flux dips are correlated with changes in the 
		background level -- in this case, they are not.
		The standard deviation and TESS magnitude are quoted in the upper right.
		The red line in the second from the top plot is the windowed 
		spline described in Section~\ref{subsec:ctois} -- in this case it is near its maximal
		frequency.
		\label{fig:pg2}
	}
\end{figure*}

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page03.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf Transit diagnostics.} The plots show the
    maximally-detrended light curve (top); the phase-folded light
    curve centered over $\pm3$ transit durations of the primary
    transit (middle left); the secondary eclipse (middle right); the
    odd-numbered transits (lower left); and the even-numbered transits
    (lower right).
    The stellar parameters ($T_{\rm eff}, R_\star, M_\star$) are taken from
    TICv8 when available \citep{stassun_TIC8_2019}.
    %Gaia-DR2 Apsis pipeline results when available
    %\citep{andrae_apsis_2018}.
    The first eight lines of text are parameters determined from the
    best-fitting TLS model.
    The one exception is the planet radius, which uses the stellar
    radius as noted above.
    The ``flux contamination'' (\texttt{TICCONT}) from neighboring
    stars is {\it never} taken into account, because transit depth
    dilution does not affect image subtraction analyses in the same
    manner as aperture-photometry reductions.
    To estimate the transit to occulation depth ratio, the
    phase-folded light curve is also coarsely fit via maximum
    likelihood by a sum of two gaussians.
    ``AstExc'' refers to the Gaia-DR2 astrometric excess, which can
    indicate hints of astrometric binarity in the system.
    ``$d_{\rm geom}$'' is the geometric distance from
    \citet{bailer-jones_distances_2018}.
    ``$R_\star + M_\star \rightarrow T_{b0}$'' gives the duration of a
    zero-eccentricity central transit based on the TICv8 stellar
    radius and mass if available. If the mass is not available, a
    stellar mass is interpolated from the
    \citet{pecaut_intrinsic_2013} table, under the assumption that the
    star is a dwarf.
    %\footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt}}.
		\label{fig:pg3}
	}
\end{figure*}

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page04.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Light curves for increasing aperture sizes.} 
		Apertures of radius 1, 1.5, and 2.25 pixels are shown from top to bottom.
		The blue line is the reference transit depth from the best-fitting TLS model.
		Any changes in depth with aperture size might indicate the need for a 
		detailed pixel-level analysis.
		\label{fig:pg4}
	}
\end{figure*}

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page05.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Cluster membership assessment diagnostics.}
		The star was considered a candidate cluster member by the source(s) listed under
		``Reference'', in this case \citet{dias_proper_2014}.
		The name used in the Dias catalog in this case was \texttt{264-025831}, a
		UCAC-4 identifier, which can be back-referenced to find that \citet{dias_proper_2014}
		assigned this star a
		membership probability in NGC 2546 of 98\%.
		The base catalog for the plots is chiefly that of \citet{Kharchenko_et_al_2013},
		due to its homogeneous parameter determination procedure (particularly for age).
		If a match to the \citet{Kharchenko_et_al_2013} catalog is found, then the remaining
		plots are populated.
		Top-left shows the parallax, with orange points sampled from the Gaia-DR2
		posterior, black points the other cluster members in the Kharchenko catalog,
		and the blue line the claimed Kharchenko parallax for the cluster.
		A large number of field contaminants are visible in this case.
		Top-right are the Gaia proper motions, where against black points are cluster
		members from Kharchenko, and the orange is the target star.
    Bottom-left is the color-magnitude diagram, and bottom-right are
    the on-sky positions.  In the text,
		\texttt{N1sr2} is the number of $1\sigma$ cluster members reported
		by \citet{Kharchenko_et_al_2013} within the cluster angular radius;
		$\log t$ is the base-10 logarithm of the age in years;
		\texttt{type} matches the type codes provided by
    \citet{Kharchenko_et_al_2013};
    \texttt{K13Note} gives the description of the cluster from
    \citet{Kharchenko_et_al_2013}, if available.
		\label{fig:pg5}
	}
\end{figure*}

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page06.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Imaging variability diagnostics.} 
		This page is intended to help diagnose which stars are producing the observed
		variability.
		Top-left and top-center are the mean out-of-transit (OOT) and mean in-transit 
		calibrated images (separate from any of our image-subtraction analysis).
		The OOT images are based on the same number of exposures as the in-transit images
		and split evenly before and after each transit \citep[following][]{bryson_identification_2013,kostov_l9859_2019}.
		The yellow star is the target; cyan dots are the flux-weighted centroid of the entire
		image for each transit event; small red crosses are WCS-projected locations of neighbor stars.
		Middle-left is the most important sub-panel: the difference between
		the OOT and in-transit mean images.
		If the variability shown in background map (units: ADU) is off-target, the
		transit is typically not from the target star.
		Middle-center is the same, normalized by the uncertainty map.
		Lower left and lower center show the DSS field in linear and log scales
		at roughly the same pixel scale as the TESS image,
		with the 1, 1.5, and 2.25 pixel-radius apertures in blue, orange, and green respectively.
		The brightness of neighborhood stars is given on the far right.
		Note the slight rotation difference between DSS and TESS images;
		DSS images are aligned north-up, east-left; TESS images are oriented as closely as
		possible to this system without actually performing the rotation.
		\label{fig:pg6}
	}
\end{figure*}

>>>>

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{epdparams_vs_time.png}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		Timeseries of ``external parameters'' for a representative
			star over one sector.
			{\it Top}: Instrumental raw magnitude (with a particular
		aperture size), as a function of time.  {\it Second and third from
			top}: $x$ and $y$ centroid positions as a function of time.
		Continuing in order are the CCD temperature, the $(s,d,k)$ shape
		parameters, and the measured background value.
		Most of the apparent variability is instrumental.
		\label{fig:external_parameter_timeseries}
	}
\end{figure}

The preceding steps produce light curves that include both
instrumental systematics as well as astrophysical variability.
Figure~\ref{fig:lc_systematics} shows twenty stars of
comparable brightness randomly selected from two CCDs.  Stars that are
far apart on the same CCD share similar changes in flux.
In other words, the instrumental systematics seem to dominate.
This problem is generic to most wide-field photometric datasets, including
those from {\it e.g.}, the WASP, HAT, and Kepler surveys.
To remove the systematic variability, we adopted two different
approaches: {\it (i)} the trend-filtering algorithm (TFA,
\citealt{kovacs_trend_2005}), and {\it (ii)} a principal component analysis
(PCA).

However, a number of other approaches to the problem
were possible. To encourage
future improvements, we describe the
possibility of decorrelating against external parameters
(\S~\ref{subsubsec:external}), and also describe different approaches
to ensemble detrending (\S~\ref{subsubsec:ensemble}), before
explaining our implementation.

\subsubsection{Decorrelating against external parameters}
\label{subsubsec:external}

Often, ensemble trends of stellar magnitude with CCD position,
sub-pixel position, catalog magnitude, and color are present in
datasets.  One detrending step that can be valuable is to fit and
subtract a linear combination of these trends as they appear across
many light curves \citep[{\it
e.g.},][\S~5.5]{zhang_precision_2016}.

A separate step for each light curve can then be to fit out linear
correlations of stellar magnitude with ``external parameters'' (EPD,
\citealt[][]{bakos_2010,huang_high-precision_2015}).  For ground-based
data these parameters might include zenith angle, or changing PSF shape.  For
TESS data, they might include CCD temperature, or the angles of the
Moon and Earth relative to each camera's boresight.  
They might also include the standard deviation of the spacecraft
quartnerion time-series \citep{vanderburg_hr858_2019}.
Some example ``external'' parameters that we include with our light
curves are shown as functions of time in
Figure~\ref{fig:external_parameter_timeseries}.

We explored the possibility of fitting linear models of flux as
functions of {\it e.g.,} temperature, shape parameters, and centroid
positions to each light curve.  We also briefly explored non-linear
model fitting using $N$-dimensional B-splines to fit the flux,
centroid positions, and temperatures simultaneously
\citep{dierckx_curve_1996}.  The linear models typically underfit the
light curves, particularly during the large shifts that happen as the
spacecraft nears perigee.  The non-linear models showed some promise,
but often seemed to overfit stellar variability signals.  Given these
complications, for the time being we omitted the step of ``detrending''
as a function of external parameters. To enable further exploration of
the issue, we included all the necessary vectors of {\it e.g.},
centroid positions, temperatures, and shape parameters in our reported
light curves.

\subsubsection{Ensemble detrending}
\label{subsubsec:ensemble}

The parameters that capture systematic trends are often poorly known.
In such cases, an effective model of the systematics comes from
constructing a set of vectors that empirically captures trends common
to many stars.  Each target light curve is then assumed to be a linear
combination of the trend vectors.

The well-known algorithms, TFA, Sys-Rem, PDC-MAP, and ARC2, all take
slightly different approaches to constructing this set of basis
vectors, as well as to solving for the weights to assign each linear
component
\citep{kovacs_trend_2005,tamuz_correcting_2005,smith_pdc_2012,aigrain_robust_2017}.
TFA selects individual ``template stars'' as basis vectors, and
equally weights each template when solving for the coefficients via
linear least squares.  PDC-MAP computes ``co-trending basis vectors''
(CBVs) by applying singular value decomposition to the light curves
that show the strongest mutual correlation.  It solves for the
coefficients through a two-step procedure.  The first step is to
calculate the coefficients through linear least squares.  The
least-squares coefficients are then used to construct a prior over
plausible coefficient values, which is then used to recompute the
maximum likelihood coefficients for each star.  This latter step
reduces overfitting for stars with variability not present in the set
of CBVs.

We opted to use two different detrending approaches, each aimed
at a different use case.  For transit-search related science,
we used TFA, as implemented by \texttt{VARTOOLS}
\citep{kovacs_trend_2005,Hartman_Bakos_2016}.  For stellar
astrophysics related work, we used a simple variant of PCA, as
implemented in \texttt{scikit-learn} \citep{sklearn_2011}.  For
self-consistency, we describe each method and its implementation in
the following paragraphs.

\paragraph{TFA detrending}

The idea of TFA is as follows.  Suppose we have $M$ ``template
stars'', which are a subsample of stars that represent all types of
systematics across the dataset.  Each template star has a light curve
with $N$ data points.  Denote the template time-series $X_j(i)$, where
$j={1,\ldots,M}$ and $i={1,\ldots,N}$ is the time index.  We then want
to find periodic signals in a target time-series $Y(i)$.  This is done
by defining a filter function
\begin{equation}
  F(i) = \sum_{j=1}^{M} c_j X_j(i),
\end{equation}
for which the coefficients $c_j$ are found by minimizing
\begin{equation}
  \mathcal{D} = \sum_{i=1}^{N} \left[ Y(i) - A(i) - F(i) \right]^2.
  \label{eq:tfa_to_minimize}
\end{equation}
When trying to find periodic signals, $A(i)$ represents our prior
knowledge of the light curve's shape.  This prior is simply that stars
on average maintain a constant brightness:
\begin{equation}
  A(i) = \langle Y \rangle = \frac{1}{N} \sum_{i=1}^{N} Y(i) = {\rm const.}
\end{equation}
If a signal is eventually found, for instance using the box-least
squares method \citep{kovacs_box-fitting_2002}, this detrending
process must then be repeated while accounting for our updated
knowledge about the light curve's shape.

\paragraph{PCA detrending}

To remove the largest systematic trends with minimal overfitting of
{\it e.g.}, stellar rotation signals, we adopted a simple variant of PCA
(see {\it e.g.}, \citealt{ivezic_statistics_2014} for a review).  A similar
approach was taken by \citet{feinstein_eleanor_2019} in
\texttt{eleanor}.  We derived the principal components for each CCD
using the 200 template stars previously selected for TFA.
We then modelled each target light curve as a linear combination of a
subset of these principal components, with weights determined by
linear least squares.

To determine the ``optimal'' number of principal components to use, we
performed a cross-validation analysis on the template stars using the
components derived both from PCA, as well as a separate factor
analysis.  As is typically the case when the noise variance is
different for each ``feature'' (each point in time), we found that
$k$-folding cross-validation using PCA failed to recover a plausible
number of components\footnote{See for example
\url{https://scikit-learn.org/stable/auto_examples/decomposition/plot_pca_vs_fa_model_selection.html}}.
However, the factor analysis typically maximized the cross-validation
score with anywhere from $10$ to $15$ components, which agreed with a
visual analysis of the number of PCA components past which overfitting
began.  We therefore used the maximum cross-validation score 
from thefactor analysis
as the number of principal components to use in each light curve.
This number is
documented in the \texttt{FITS} headers of each light curve.

@@

@@

Figures~\ref{fig:pg1} to~\ref{fig:pg6} of this
section summarize this document. Updated versions and their 
\texttt{README} files will live at this web-address: 
\url{mast.stsci.edu/CDIPS}.
The planet candidate chosen for these figures
(Gaia-DR2 \texttt{5541111035713815552} = TIC \texttt{110718787}) was
chosen for the demonstration in part because it passes all
the tests.
It is one of a number of the giant planet candidates that we note may
be in open clusters.

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.98\textwidth]{gaiatwo0005599752663752776192-0007_page01.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Transit search summary.}
    Periodograms from TLS and phase-dispersion minimization, as
    calculated with \texttt{astrobase.periodbase}, are shown in the
    top left and top center
    \citep{bhatti_astrobase_2018,hippke_TLS_2019,stellingwerf_period_1978}.
    The top three peaks from each method are shown in the second and
    third rows; the raw light curve is in the top-right. A small
    finder chart from DSS is inset to the top left, with the 1.5-pixel
    radius aperture used to extract the light curve in orange.
		\label{fig:pg1}
	}
\end{figure*}

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.98\textwidth]{gaiatwo0005599752663752776192-0007_page02.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Light curve diagnostics.} 
    Time-series of raw flux (\texttt{IRM2}),  TFA-detrended flux
    (\texttt{TF2}), stellar-variability detrended flux, and the
    background are shown as a function of barycentric Julian date.
    The overplotted dashed vertical lines are the ephemeris of the
    highest-power TLS peak from Figure~\ref{fig:pg1}.
    An important check is whether the flux dips are correlated with
    changes in the background level -- in this case, they are not.
    The standard deviation and TESS magnitude are quoted in the upper
    right.  The red line in the second from the top plot is the
    windowed spline described in Section~\ref{subsec:ctois}, in this
    case an essential step for finding the eclipse signal.
		\label{fig:pg2}
	}
\end{figure*}

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.98\textwidth]{gaiatwo0005599752663752776192-0007_page03.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf Transit diagnostics.}
    The plots show the maximally-detrended light curve (top); the
    phase-folded light curve centered over $\pm3$ transit durations of
    the primary transit (middle left); the secondary eclipse (middle
    right); the odd-numbered transits (lower left); and the
    even-numbered transits (lower right).
    The stellar parameters ($T_{\rm eff}, R_\star, M_\star$) are taken
    from TICv8 when available \citep{stassun_TIC8_2019}.
    %Gaia-DR2 Apsis pipeline results when available
    %\citep{andrae_apsis_2018}.
    The first eight lines of text are parameters determined from the
    best-fitting TLS model.  The one exception is the planet radius,
    which uses the stellar radius as noted above.
    The ``flux contamination'' (\texttt{TICCONT}) from neighboring
    stars is {\it never} taken into account, because transit depth
    dilution does not affect image subtraction analyses in the same
    manner as aperture-photometry reductions.
    The significance of the odd-to-even asymmetry is quoted,
    but given the strong rotational variability in this object (Figure~\ref{fig:pg2}),
   	the apparent odd-even asymmetry could have been caused by the detrending process.
    To estimate the transit to occulation depth ratio $\delta_{\rm tra}/\delta_{\rm occ}$,
    the phase-folded light curve is also fit by a sum of two
    gaussians (in this case, the fit failed).
    ``AstExc'' refers to the Gaia-DR2 astrometric excess, which can
    indicate hints of astrometric binarity in the system.
    ``$d_{\rm geom}$'' is the geometric distance from
    \citet{bailer-jones_distances_2018}.
    ``$R_\star + M_\star \rightarrow T_{b0}$'' gives the duration of a
    zero-eccentricity central transit based on the TICv8 stellar
    radius and mass if available. If the mass is not available, a
    stellar mass is interpolated from the
    \citet{pecaut_intrinsic_2013} table, under the assumption that the
    star is a dwarf.
    %\footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt}}.
		\label{fig:pg3}
	}
\end{figure*}

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.98\textwidth]{gaiatwo0005599752663752776192-0007_page04.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Light curves for increasing aperture sizes.} 
    Apertures of radius 1, 1.5, and 2.25 pixels are shown from top to
    bottom.  The blue line is the reference transit depth from the
    best-fitting TLS model.  Changes in depth with increasing aperture size
    can indicate that the source of variability is off-center from the 
    aperture, suggesting a photometric blend.
		\label{fig:pg4}
	}
\end{figure*}

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.98\textwidth]{gaiatwo0005599752663752776192-0007_page05.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Cluster membership assessment diagnostics.}
    The star was considered a candidate cluster member by the
    source(s) listed under ``Reference'', in this case
    \citet{cantat-gaudin_gaia_2018}.  The name used in their catalog
    in this case was \texttt{5599752663752776192}, a Gaia-DR2
    identifier, which can be back-referenced to find that
    \citet{cantat-gaudin_gaia_2018} assigned this star a membership
    probability in Haffner 13 of just 10\%.
    The base catalog for the plots is chiefly that of
    \citet{Kharchenko_et_al_2013}, due to its homogeneous parameter
    determination procedure (particularly for age).  If a match to the
    \citet{Kharchenko_et_al_2013} catalog is found, then the remaining
    plots are populated.  Top-left shows the parallax, with orange
    points sampled from the Gaia-DR2 posterior, black points the other
    cluster members in the Kharchenko catalog, and the blue line the
    claimed Kharchenko parallax for the cluster.  A number of
    field contaminants in the Kharchenko catalog are visible in this
    case.  Top-right are the Gaia proper motions, where against black
    points are cluster members from Kharchenko, and the orange is the
    target star.  Bottom-left is the color-magnitude diagram, and
    bottom-right are the on-sky positions.  In the text,
    \texttt{N1sr2} is the number of $1\sigma$ cluster members reported
    by \citet{Kharchenko_et_al_2013} within the cluster angular
    radius; $\log t$ is the base-10 logarithm of the age in years;
    \texttt{type} matches the type codes provided by
    \citet{Kharchenko_et_al_2013}; \texttt{K13Note} gives the
    description of the cluster from \citet{Kharchenko_et_al_2013}, if
    available.
    Extra caution must be taken when interpreting this set of plots,
    since they can only show disagreement between the observed star's
    properties and those of the listed Kharchenko members (and the
    latter may be biased).
		\label{fig:pg5}
	}
\end{figure*}

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.98\textwidth]{gaiatwo0005599752663752776192-0007_page06.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Imaging variability diagnostics.} 
    This page is intended to help diagnose which stars are producing
    the observed variability.  Top-left and top-center are the mean
    out-of-transit (OOT) and mean in-transit calibrated images
    (separate from any of our image-subtraction analysis).  The OOT
    images are based on the same number of exposures as the in-transit
    images and split evenly before and after each transit
    \citep[following][]{bryson_identification_2013,kostov_l9859_2019}.
    The yellow star is the target; cyan dots are the flux-weighted
    centroid of the entire image for each transit event; small red
    crosses are WCS-projected locations of neighbor stars.
    Middle-left is the most important sub-panel: the difference
    between the OOT and in-transit mean images.  If the variability
    shown in background map (units: ADU) is off-target, the transit is
    typically not from the target star.  Middle-center is the same,
    normalized by the uncertainty map.  Lower left and lower center
    show the DSS field in linear and log scales at roughly the same
    pixel scale as the TESS image, with the 1, 1.5, and 2.25
    pixel-radius apertures in blue, orange, and green respectively.
    The brightness of neighborhood stars is given on the far right.
    Note the slight coordinate rotation difference between DSS and TESS images;
    DSS images are aligned north-up, east-left; TESS images are
    oriented as closely as possible to this system without actually
    performing the rotation.
		\label{fig:pg6}
	}
\end{figure*}

% \begin{figure*}[!h]
% 	\begin{center}
% 		\leavevmode
% 		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page01.pdf}
% 	\end{center}
% 	\vspace{-0.5cm}
% 	\caption{
% 		{\bf Transit search summary.} Periodograms from TLS and 
% 		phase-dispersion minimization, as calculated 
% 		with \texttt{astrobase.periodbase}, are shown in the top left and top center 
% 		\citep{bhatti_astrobase_2018,hippke_TLS_2019,stellingwerf_period_1978}.
% 		The top three peaks from each 
% 		method are shown in the second and third rows; the raw light curve is in the 
% 		top-right. A small finder chart from DSS is inset to the top left, with
% 		the 1.5-pixel radius aperture used to extract the light curve in orange.
% 		\label{fig:pg1}
% 	}
% \end{figure*}
% \begin{figure*}[!h]
% 	\begin{center}
% 		\leavevmode
% 		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page02.pdf}
% 	\end{center}
% 	\vspace{-0.5cm}
% 	\caption{
% 		{\bf Light curve diagnostics.} 
% 		Time-series of raw flux (\texttt{IRM2}),  TFA-detrended flux (\texttt{TF2}), stellar-variability
% 		detrended flux, and the background are shown as a function of
% 		barycentric Julian date.
% 		The overplotted dashed vertical lines are the ephemeris of the highest-power
% 		TLS peak from Figure~\ref{fig:pg1}.
% 		An important check is whether the flux dips are correlated with changes in the 
% 		background level -- in this case, they are not.
% 		The standard deviation and TESS magnitude are quoted in the upper right.
% 		The red line in the second from the top plot is the windowed 
% 		spline described in Section~\ref{subsec:ctois} -- in this case it is near its maximal
% 		frequency.
% 		\label{fig:pg2}
% 	}
% \end{figure*}
% \begin{figure*}[!h]
% 	\begin{center}
% 		\leavevmode
% 		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page03.pdf}
% 	\end{center}
% 	\vspace{-0.5cm}
% 	\caption{
%     {\bf Transit diagnostics.} The plots show the
%     maximally-detrended light curve (top); the phase-folded light
%     curve centered over $\pm3$ transit durations of the primary
%     transit (middle left); the secondary eclipse (middle right); the
%     odd-numbered transits (lower left); and the even-numbered transits
%     (lower right).
%     The stellar parameters ($T_{\rm eff}, R_\star, M_\star$) are taken from
%     TICv8 when available \citep{stassun_TIC8_2019}.
%     %Gaia-DR2 Apsis pipeline results when available
%     %\citep{andrae_apsis_2018}.
%     The first eight lines of text are parameters determined from the
%     best-fitting TLS model.
%     The one exception is the planet radius, which uses the stellar
%     radius as noted above.
%     The ``flux contamination'' (\texttt{TICCONT}) from neighboring
%     stars is {\it never} taken into account, because transit depth
%     dilution does not affect image subtraction analyses in the same
%     manner as aperture-photometry reductions.
%     To estimate the transit to occulation depth ratio, the
%     phase-folded light curve is also coarsely fit via maximum
%     likelihood by a sum of two gaussians.
%     ``AstExc'' refers to the Gaia-DR2 astrometric excess, which can
%     indicate hints of astrometric binarity in the system.
%     ``$d_{\rm geom}$'' is the geometric distance from
%     \citet{bailer-jones_distances_2018}.
%     ``$R_\star + M_\star \rightarrow T_{b0}$'' gives the duration of a
%     zero-eccentricity central transit based on the TICv8 stellar
%     radius and mass if available. If the mass is not available, a
%     stellar mass is interpolated from the
%     \citet{pecaut_intrinsic_2013} table, under the assumption that the
%     star is a dwarf.
%     %\footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt}}.
% 		\label{fig:pg3}
% 	}
% \end{figure*}
% \begin{figure*}[!h]
% 	\begin{center}
% 		\leavevmode
% 		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page04.pdf}
% 	\end{center}
% 	\vspace{-0.5cm}
% 	\caption{
% 		{\bf Light curves for increasing aperture sizes.} 
% 		Apertures of radius 1, 1.5, and 2.25 pixels are shown from top to bottom.
% 		The blue line is the reference transit depth from the best-fitting TLS model.
% 		Any changes in depth with aperture size might indicate the need for a 
% 		detailed pixel-level analysis.
% 		\label{fig:pg4}
% 	}
% \end{figure*}
% \begin{figure*}[!h]
% 	\begin{center}
% 		\leavevmode
% 		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page05.pdf}
% 	\end{center}
% 	\vspace{-0.5cm}
% 	\caption{
% 		{\bf Cluster membership assessment diagnostics.}
% 		The star was considered a candidate cluster member by the source(s) listed under
% 		``Reference'', in this case \citet{dias_proper_2014}.
% 		The name used in the Dias catalog in this case was \texttt{264-025831}, a
% 		UCAC-4 identifier, which can be back-referenced to find that \citet{dias_proper_2014}
% 		assigned this star a
% 		membership probability in NGC 2546 of 98\%.
% 		The base catalog for the plots is chiefly that of \citet{Kharchenko_et_al_2013},
% 		due to its homogeneous parameter determination procedure (particularly for age).
% 		If a match to the \citet{Kharchenko_et_al_2013} catalog is found, then the remaining
% 		plots are populated.
% 		Top-left shows the parallax, with orange points sampled from the Gaia-DR2
% 		posterior, black points the other cluster members in the Kharchenko catalog,
% 		and the blue line the claimed Kharchenko parallax for the cluster.
% 		A large number of field contaminants are visible in this case.
% 		Top-right are the Gaia proper motions, where against black points are cluster
% 		members from Kharchenko, and the orange is the target star.
%     Bottom-left is the color-magnitude diagram, and bottom-right are
%     the on-sky positions.  In the text,
% 		\texttt{N1sr2} is the number of $1\sigma$ cluster members reported
% 		by \citet{Kharchenko_et_al_2013} within the cluster angular radius;
% 		$\log t$ is the base-10 logarithm of the age in years;
% 		\texttt{type} matches the type codes provided by
%     \citet{Kharchenko_et_al_2013};
%     \texttt{K13Note} gives the description of the cluster from
%     \citet{Kharchenko_et_al_2013}, if available.
% 		\label{fig:pg5}
% 	}
% \end{figure*}
% \begin{figure*}[!h]
% 	\begin{center}
% 		\leavevmode
% 		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page06.pdf}
% 	\end{center}
% 	\vspace{-0.5cm}
% 	\caption{
% 		{\bf Imaging variability diagnostics.} 
% 		This page is intended to help diagnose which stars are producing the observed
% 		variability.
% 		Top-left and top-center are the mean out-of-transit (OOT) and mean in-transit 
